Testing the Relationship between Phenomenological Control related to Illusion Sensitivity

### 2025-04-22 paper/R1/manuscript.qmd
changes made to manuscript

Visual Illusions are an interesting type of stimuli highlighting the ease with which our phenomenological conscious experience can become dissociated from physical reality. 
Their robust and reliable effect makes them useful stimuli to explore how perception is constructed and shaped, and several theoretical models have been put forth to explain how they work. 
**In particular, illusions have been reframed using a predictive coding account of perception [@notredame2014] in which the brain optimally combines, using some flavour of Bayesian inference, perceptual inputs with prior knowledge to make sense of ambiguous environments [@friston2010].**

@@

The "Illusion Game" paradigm [@makowski2023] has been recently developed to measure illusion sensitivity to various illusion types through its behavioural impact (on response time and error rate) in a perceptual decision task (where participants have to respond as fast as possible; e.g., "which of the left or right circles is bigger"). 
The stimuli for different classical illusions are created using the *Pyllusion* software [@makowski2021], which allows researchers to modulate the strength of the illusion as a continuous dimension, independently from the difficulty of the perceptual task. 
This paradigm, inspired by psychophysics, lends itself to the computational modelling of illusion sensitivity through its interference effect, hopefully bypassing some of the metacognitive processes at stake in other paradigms.

Interestingly, the fact that inter-individual variability in illusion sensitivity seems to persist in this task suggests that it is not solely explained by **metacognitive ability differences**, and gives rise to the following question: is the variability in illusion sensitivity related to low-level perceptual processes (e.g., baseline precision of perceptual priors), or rather to the ability to actively control and "resist" the illusion in a **top-down** fashion in order to achieve the task at hand (higher-level modulation of the perceptual inference parameters). 
If the latter is true, then illusion sensitivity measured in contexts with strong task-demand characteristics, e.g., in paradigms where participants' performance is explicitly or implicitly assessed (i.e., where there is an incentive to downplay the illusion effect) might correlate with one's ability to alter one's subjective experience following suggestions - a mechanism referred to as "phenomenological control".

@@

To encourage the empirical exploration of our ability and tendency to alter our phenomenological experience and further accelerate investigations away from the hypnotic context, @lush2021 adapted the Sussex-Waterloo Scale of Hypnotisability [SWASH, @lush2018] by removing all its references to hypnosis, to measure trait phenomenological control. 
**This newly developed phenomenological control scale (PCS) consists of 10 imaginative suggestions followed by subjective ratings for each suggestion on a 6-point Likert scale (from 0-5) and has demonstrated validity in online experiments [@lush2022].**

Interestingly, @lush2022 did test for a relationship between PC and illusion sensitivity using the Müller-Lyer illusion (in which the arrangement of the arrowheads flanking two lines makes them appear as having different lengths), and reported evidence in favour of an absence of correlation between the two measures. 
This finding was interpreted as indicative of the cognitive impenetrability of illusions, implying that the effect is driven by low-level processes and therefore not influenced by top-down mechanisms such as PC. 
The goal of this study is thus to replicate the results from @lush2022 pointing to an absence of a relationship between phenomenological control and illusion sensitivity, by generalising them to a different illusion paradigm that encompasses other illusion types (see @tbl-table1).

::: {#tbl-table1}
```{r}
#| tbl-cap: "Study Design Table"

question <- c("Question", "Hypothesis", "Sampling Plan", "Analysis Plan", "Rationale for Deciding the Sensitivity of the Test", "Interpretation Given Different Outcomes", "Theory That Could Be Shown Wrong by the Outcomes")
answer <- c("Is there a correlation between trait phenomenological control (PC) and visual illusion (VI) sensitivity?", "Replicating findings from Lush et al., 2022 paper, we expect evidence to support the absence of a relationship between VI and PCS", "The goal is to recruit around 500 adult English speakers using Prolific. This sample size is based on the ones used in Lush et al., 2021 and Lush et al., 2022 that we aim at replicate.", "Bayesian correlations between the PC score and the VI performance for the 3 illusion types (corresponding to the error rate) will be computed using the BayesFactor::BFCorrelation() function (with the r-scale prior parameter set to ‘medium’)", "Evidence against a relationship between PC and VI will be found if BF10 <= 1/3, following the Lush et al., 2022 findings, for all three illusions. BF10 > 3 will be interpreted as evidence for a relationship between these two measures.", "The hypothesis that VI sensitivity is independent from PC.", "The cognitive impenetrability of illusions, implying that the effect is driven by low-level processes and therefore not influenced by top-down mechanisms such as PC.")

@@

Study Design Table
:::

@@

Participants will be presented with a consent form followed by demographic questions (gender, education level, age, and ethnicity). 
**Although these variables are not directly analyzed in the current study, they will be used to provide to provide a detailed and thorough description of the sample and maximizing data reusability.** 
Participants will then be administered the PCS and the Illusion Game task (IG) in a counterbalanced order.

@@

The task is an adaptation of the one used in @makowski2023 to make it shorter and more reliable, in which participants must make perceptual judgments (e.g., "which red line is the longer") as quickly and accurately as possible. It includes 3 illusion types, namely Ebbinghaus, Müller-Lyer, and Vertical-Horizontal. 
The procedure encompasses 2 sets of 80 trials for each illusion type. 
Each set will include, in a random order, the 3 blocks of illusion types, in which trials are separated by a fixation cross, temporally (uniformly sampled duration of 500 - 1000s) and spatially jittered (around the centre of the screen in a radius of a 1 cm) to attenuate its potential usefulness as a reference point. 
After each illusion type block, a score is presented (computed as a scaled Inverse Efficiency Score) as a gamification mechanism to increase motivation to perform to the best of one's abilities. 
To mitigate for the potential variability in the speed/accuracy trade-off, the instructions emphasize with equal weight to be fast and to avoid errors.

```{r}
#| warning: false
#| label: "fig-illusion_framework"
#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"
#| fig-cap: "The parametric framework for visual illusions (Makowski et al., 2021) applied to the Müller-Lyer illusion (above). Below are examples of stimuli showcasing the manipulation of two parameters, task difficulty and illusion strength."

knitr::include_graphics("img/example_stimuli.png")
```

For each illusion type, two continuous dimensions are orthogonally manipulated [see @makowski2021 for details on the rationale and execution], namely task difficulty and illusion strength, so that each trial corresponds to a unique combination. 
Task difficulty corresponds to the difficulty of the perceptual decision (e.g., if the task is to select the longest red line, task difficulty corresponds to how the lines are objectively different). 
Illusion strength corresponds to the degree to which the illusion elements (e.g., the black arrow lines in Müller-Lyer) are interfering with the aforementioned task. 
Note that the illusion effect can be "incongruent" (biasing perception in the direction of the incorrect response) or "congruent" (facilitating, i.e., biasing perception in the direction of the correct response). 
Participants respond with a key arrow (left vs. right; or up vs. down), and their reaction time (RT) and accuracy are recorded.

Visual illusion sensitivity will be measured as the average error rate in the incongruent condition, separately for the 3 illusion types. 
Although the error rate is arguably a crude score, which does not take into account the effect of varying illusion strength, the interaction with task difficulty and the possible adjustments in response strategy (speed-accuracy trade off), it is also the most simple and easy to reproduce, hence its usage as our primary outcome for the current **registered report**.

The two sets of 3 illusion blocks will be separated by 2 short questionnaires acting as a break, namely the IPIP-6 [@sibley2011mini], measuring 6 personality traits with 24 analogue scales items, and the PID-5 [@krueger2011], measuring 5 maladaptive personality traits with 25 Likert scales items. 
These questionnaires are included as a way of providing a break between the two cognitively taxing blocks and maintain paradigmatic consistency with previous studies [@makowski2023].

```{r}
#| warning: false
#| label: "fig-illusionexample"
#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"
#| fig-cap: "The study involved three visual illusions, in which participants were instructed to respond as quickly as possible without making errors. Each illusion included two manipulated parameters: strength (e.g., the angle of the outward- or inward-pointing arrow-like fins in the Müller-Lyer illusion) and difficulty (e.g., the difference in line lengths in the Müller-Lyer illusion."

@@

@@

The PCS will contain several manipulation check indices to identify problematic participants. 
**The phenomenological control task consists of various auditory and visual exercises.**
**In one such exercise, participants receive the following instruction: “Open your eyes. You will see only two balls on the screen…just two balls”.**
**However, three differently coloured balls are actually displayed.**
**If participants select the option "no balls were shown", it indicates they failed to pay attention to both the auditory instructions and the visual stimuli.**
**In another exercise, participants are asked to press the spacebar six times.**
**If they press it fewer than five times within the allotted time, it suggests a lack of attentiveness to the auditory instructions.**
**Participants will be excluded if they fail at least one of these checks. Participants will be excluded if they fail at least one of the attention checks.**

Illusion Game outliers will be flagged based on their RT distributions, following the same procedure as in [@makowski2023]. 
**If the RT is collapsed to the left (i.e., has \> 1/3 of ultra-fast responses - typically \< 200 ms) in the first set, the entire participant will be discarded (suggesting that they did not properly do the task), but if only the second set is bad, then only the second set will be discarded (as the illusion sensitivity can still be estimated, albeit with less precision).** 
In addition, the removal of individual trials will also be performed [RT \< 200 ms or \> 3 SD; following @theriault2024].

After removing problematic participants and trials, the outcome measures (PC and VI sensitivity scores) will be computed and the Bayesian correlation (with medium prior on the coefficient, i.e., r-scale parameter set to 1/3) will be computed [using the *BayesFactor* package; @BayesFactor]. 
Following @lush2022, we expect to collect evidence against (BF10 \<= 1/3) a relationship between PCS and VI sensitivity. 
Data analysis will be carried out using R, using *tidyverse* [@tidyverse] and *easystats* [@easystats; @parameters; @correlation; @bayestestR; @datawizard]. 
The analysis script and additional information are available at *https://github.com/RealityBending/IllusionGamePhenomenologicalControl*.

@@

All the study materials, experiment, data, and analysis is available on GitHub at https://github.com/RealityBending/IllusionGamePhenomenologicalControl

>>>>

Visual Illusions are an interesting type of stimuli highlighting the ease with which our phenomenological conscious experience can become dissociated from physical reality. 
Their robust and reliable effect makes them useful stimuli to explore how perception is constructed and shaped, and several theoretical models have been put forth to explain how they work. 
**In particular, illusions have been reframed using a predictive coding account of perception [e.g., @notredame2014; @nour2015perception]** in which the brain optimally combines, using some flavour of Bayesian inference, perceptual inputs with prior knowledge to make sense of ambiguous environments [@friston2010].

@@

```{r}
#| warning: false
#| label: fig-illusion_framework
#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"
#| fig-cap: "The parametric framework for visual illusions (Makowski et al., 2021) applied to the Müller-Lyer illusion. Below are examples of stimuli showcasing the manipulation of two parameters, task difficulty and illusion strength."

knitr::include_graphics("img/IG_framework.png")
```

The "Illusion Game" paradigm [@makowski2023] has been recently developed to measure illusion sensitivity to various illusion types through its behavioural impact (on response time and error rate) in a perceptual decision task (where participants have to respond as fast as possible; e.g., "which of the left or right circles is bigger"). 
The stimuli for different classical illusions are created using the *Pyllusion* software [@makowski2021], which allows researchers to modulate the strength of the illusion as a continuous dimension, independently from the difficulty of the perceptual task (see @fig-illusion_framework). 
This paradigm, inspired by psychophysics, lends itself to the computational modelling of illusion sensitivity through its **interference effect —an effect that disrupts an individual's ability to accurately discriminate between perceptual stimuli.**
**This approach aims to bypass some of the metacognitive processes involved in other paradigms, offering a more direct and objective measure of how illusions influence perceptual judgment.**

Interestingly, the fact that inter-individual variability in illusion sensitivity seems to persist in this task suggests that it is not solely explained by **metacognitive ability differences**, and gives rise to the following question: is the variability in illusion sensitivity related to low-level perceptual processes (e.g., baseline precision of perceptual priors), or rather to the ability to actively control and "resist" the illusion in order to achieve the task at hand (higher-level modulation of the perceptual inference parameters). 
If the latter is true, then illusion sensitivity measured in contexts with strong task-demand characteristics, e.g., in paradigms where participants' performance is explicitly or implicitly assessed (i.e., where there is an incentive to downplay the illusion effect) might correlate with one's ability to alter one's subjective experience following suggestions - a mechanism referred to as "phenomenological control".

@@

To encourage the empirical exploration of our ability and tendency to alter our phenomenological experience and further accelerate investigations away from the hypnotic context, @lush2021 adapted the Sussex-Waterloo Scale of Hypnotisability [SWASH, @lush2018] by removing all its references to hypnosis, to measure trait phenomenological control. 
**This newly developed phenomenological control scale (PCS) consists of 10 imaginative suggestions followed by subjective ratings for each suggestion and has demonstrated validity in online experiments [@lush2022].**

Interestingly, @lush2022 did test for a relationship between PC and illusion sensitivity using the Müller-Lyer illusion (in which the arrangement of the arrowheads flanking two lines makes them appear as having different lengths), and reported evidence in favour of an absence of correlation between the two measures. 
This finding was interpreted as indicative of the cognitive impenetrability of illusions, implying that the effect is driven by low-level processes and therefore not influenced by top-down mechanisms such as PC. 
**Note that both prior-knowledge and phenomenological control are considered top-down processes, but the cognitive impenetrability hypothesis suggests that the processes at stake for the illusions happen at a lower- encapsulated- level (in the form of *perceptual* priors)**.

The goal of this study is thus to replicate the results from @lush2022 pointing to an absence of a relationship between phenomenological control and illusion sensitivity, by generalising them to a different illusion paradigm that encompasses other illusion types.
**Additionally, we will explore the relationship between psychoticism, as a proxy for schizophrenia, and illusion sensitivity to assess the potential impact of lower-level effects—such as weak priors observed in individuals with schizophrenia [@costa2023]—on sensitivity to illusions.**
**These analyses may offer evidence clarifying whether inter-individual variability in illusion sensitivity is driven by lower-level perceptual mechanisms or higher-level cognitive processes (@tbl-DesignTable).**

```{r}
#| tbl-cap: "Study Design Table"
#| label: tbl-DesignTable

question <- c("Question", "Hypothesis", "Sampling Plan", "Analysis Plan", "Rationale for Deciding the Sensitivity of the Test", "Interpretation Given Different Outcomes", "Theory That Could Be Shown Wrong by the Outcomes")
answer <- c("Is there a correlation between trait phenomenological control (PC) and visual illusion (VI) sensitivity? Additionally, is there a relationship between VI sensitivity and the psychoticism facet of the PID-5, as a proxy for schizophrenia-related traits?", "In line with Lush et al. (2022), we hypothesise that there will be evidence supporting the absence of a relationship between PC and VI sensitivity. Based on Makowski et al. (2023) and prior work on weak priors in schizophrenia, we hypothesise that higher psychoticism scores will be positively associated with VI sensitivity.", "The goal is to recruit around 500 adult English speakers using Prolific. This sample size is based on the ones used in Lush et al., 2021 and Lush et al., 2022 that we aim at replicate.", "Bayesian correlations will be conducted using the BayesFactor::correlationBF() function, with a medium prior (r-scale = 1/3), separately for: 1) PC scores and VI sensitivity (error rate and IES), across all three illusion types; and 2) Psychoticism facet scores from the PID-5 and VI sensitivity scores, across all three illusion types.", "For the PC–VI sensitivity relationship, we will interpret BF₁₀ ≤ 1/3 as evidence against a relationship, in line with Lush et al. (2022). For the psychoticism–VI sensitivity relationship, BF₁₀ > 3 will be interpreted as evidence supporting a relationship, following findings by Makowski et al. (2023).", "If there is no evidence for a PC–VI relationship across all three illusions, it would support the hypothesis that VI sensitivity is independent from PC. If a positive association is found between psychoticism and VI sensitivity, it may suggest a low-level perceptual basis for inter-individual differences in illusion sensitivity.", "The cognitive impenetrability of visual illusions, which posits that illusion sensitivity is driven solely by low-level processes and is not influenced by top-down mechanisms such as phenomenological control. Conversely, a lack of association with psychoticism would challenge the view that low-level perceptual alterations underlie illusion sensitivity in non-clinical populations.")

@@

@@

Participants will be presented with a consent form followed by demographic questions (gender, education level, age, and ethnicity). 
**Although these variables are not directly analyzed in the current study, they will be used to provide to provide a detailed and thorough description of the sample and maximizing data reusability.** 
**Participants will then be administered the PCS and the Illusion Game task (IG) in a counterbalanced order.**

@@

The task is an adaptation of the one used in @makowski2023 to make it shorter, in which participants must make perceptual judgments (e.g., "which red line is the longer") as quickly and accurately as possible. It includes 3 illusion types, namely Ebbinghaus, Müller-Lyer, and Vertical-Horizontal (see @fig-illusionexample).

```{r}
#| warning: false
#| label: fig-illusionexample
#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"
#| fig-cap: "The study involved three visual illusions, in which participants were instructed to respond as quickly as possible without making errors. Each illusion included two manipulated parameters: strength (e.g., the angle of the outward- or inward-pointing arrow-like fins in the Müller-Lyer illusion) and difficulty (e.g., the difference in line lengths in the Müller-Lyer illusion)."

@@

**In the original Illusion Game, 10 visual illusions were presented in two sets, following a practice trial, and separated by two short questionnaires.**
**Participants completed a total of 1,340 trials, with the experiment lasting approximately 55 minutes.**
**In the current procedure, only three illusions are used, selected based on the original study's findings that these illusions most strongly contribute to illusion sensitivity.**

The procedure encompasses 2 sets of 80 trials for each illusion type, **preceded by a practice trial for each illusion**. 
Each set will include, in a random order, the 3 blocks of illusion types, in which trials are separated by a fixation cross, temporally (uniformly sampled duration of 500 - 1000s) and spatially jittered (around the centre of the screen in a radius of a 1 cm) to attenuate its potential usefulness as a reference point. 
After each illusion type block, an arbitrary score is presented (computed as a scaled Inverse Efficiency Score) as a gamification mechanism to increase motivation to perform to the best of one's abilities. 
To mitigate for the potential variability in the speed/accuracy trade-off, the instructions emphasize with equal weight to be fast and to avoid errors.

For each illusion type, two continuous dimensions are orthogonally manipulated namely task difficulty and illusion strength, so that each trial corresponds to a unique combination, **providing an objectively correct answer for each task.**
**The use of these manipulations allows concise, standardised reporting of illusion parameters and ensures our stimuli are fully reproducible [see @makowski2021].**

Task difficulty corresponds to the difficulty of the perceptual decision (e.g., if the task is to select the longest red line, task difficulty corresponds to how the lines are objectively different). 
Illusion strength corresponds to the degree to which the illusion elements (e.g., the black arrow lines in Müller-Lyer) are interfering with the aforementioned task. 
Note that the illusion effect can be either “incongruent”, **making the task more difficult by biasing perceptual decisions toward the incorrect response** or “congruent”, **making the task easier by biasing decisions toward the correct response (e.g., in the Müller-Lyer illusion, if the outwards-facing arrowheads are placed on the longer line, identifying which line is the longest becomes easier)**.
Participants respond with a key arrow (left vs. right; or up vs. down), and their reaction time (RT) and accuracy are recorded.

Visual illusion sensitivity will be measured as the average error rate in the incongruent condition, and separately for the 3 illusion types. 
Although the error rate is arguably a crude score, which does not take into account the effect of varying illusion strength, the interaction with task difficulty and the possible adjustments in response strategy (speed-accuracy trade off), it is also the most simple and easy to reproduce, hence its usage as our primary outcome for the current **registered report**.
**As a secondary exploratory outcome, the Inverse Efficiency Score [IES, @townsend2014methods] will also be computed. This metric incorporates both speed and accuracy by dividing the mean reaction time of correct responses by the proportion of correct responses, separately for each illusion.**

The two sets of 3 illusion blocks will be separated by 2 short questionnaires acting as a break, namely the IPIP-6 [@sibley2011mini], measuring 6 personality traits with 24 analogue scales items, and the PID-5 [@krueger2011], measuring 5 maladaptive personality traits with 25 Likert scales items. 
These questionnaires are included as a way of providing a break between the two cognitively taxing blocks and maintain paradigmatic consistency with previous studies [@makowski2023].
**Additionally, the psychoticism subscale of the PID-5 will be used to examine the correlation between maladaptive traits and illusion sensitivity, evaluating the existence of the link proposed in previous studies [@costa2023].**

@@

The PCS will contain several manipulation check indices to identify problematic participants. 
**The phenomenological control task consists of various auditory and visual exercises.**
**At the start of the task, participants first hear someone say "hello." They are then asked to choose from several options, including "Hello," "Goodbye," "How are you," and "Thank you".**
**Any participant who selects an option other than the correct one will be considered inattentive**
**In another exercise, participants receive the following instruction: “Open your eyes. You will see only two balls on the screen…just two balls”.**
**However, three differently coloured balls are actually displayed.**
**If participants select the option "no balls were shown", it indicates they failed to pay attention to both the auditory instructions and the visual stimuli.**
**Lastly, in another exercise, participants are asked to press the spacebar six times.**
**If they press it fewer than five times within the allotted time, it suggests a lack of attentiveness to the auditory instructions.**
**Participants will be excluded if they fail at least one of these checks.**
**Lastly, reliability of the PCS will be assessed by computing Cronbach's alpha [@cronbach1951coefficient].**

**To assess whether the illusions functioned as expected, stimuli will be categorized into three groups: Strong Illusion Strength & Incongruent, Mild Illusion Strength & Incongruent, and Congruent.**
**Two Bayesian t-tests will be conducted to assess differences in IES between the Congruent and Mild conditions, and between the Mild and Strong conditions.**
**Significant differences in these comparisons will provide evidence that the illusions functioned as intended.**

**The two outcome measures—error rate and IES—will be computed for each illusion and for each illusion strength group: Strong Illusion Strength & Incongruent, Mild Illusion Strength & Incongruent, and Congruent.**
**Correlation will be computed between the mild and strong groups for each illusion and outcomes separately.**
**If these correlations are high [*r* > .50, @cohen2013statistical], the mild and strong illusion strength groups will be collapsed and the outcomes will be recomputed across all trials, otherwise they will be treated as separate in subsequent analyses.**

**Reliability analyses will then be conducted on all resulting indices.** **First, split-half reliability, to assess internal consistency, will be computed by correlating two equal subsets of individual scores, with high correlations expected (*r* > .5).**
**Second, inter-illusion reliability will be evaluated using Cronbach’s alpha across the three illusions.**

Illusion Game outliers will be flagged based on their RT distributions, following the same procedure as in [@makowski2023]. 
**If the RT is collapsed to the left (i.e., has \> 1/3 of ultra-fast responses - typically \< 200 ms) in the first set, the entire participant will be discarded (suggesting that they did not properly do the task), but if only the second set is bad, then only the second set will be discarded (as the illusion sensitivity can still be estimated, albeit with less precision).** 
In addition, the removal of individual trials will also be performed [RT \< 200 ms or \> 3 SD; following @theriault2024].
**To mitigate the risk of confounding effects driven by extreme speed or accuracy strategies, participants whose RTs are significantly slower than the group average (RT > 4 SD above the mean, based on @makowski2023) will be excluded from the analysis.**

After removing problematic participants and trials, the outcome measures (PC and VI sensitivity scores) will be computed and the Bayesian correlation (with medium prior on the coefficient, i.e., r-scale parameter set to 1/3) will be computed [using the *BayesFactor* package, @BayesFactor].
This shifted beta prior, as recommended by @morey2018baysefactor, offers a balanced approach to estimating effect sizes, without placing undue weight on larger effect sizes or artificially inflating evidence for the null hypothesis.
Following @lush2022, we expect to collect evidence against (BF10 \<= 1/3) a relationship between PCS and VI sensitivity. 
**Additionally, Bayesian correlations will be computed using the BayesFactor package, employing a medium prior on the coefficient (r-scale parameter set to 1/3) to assess relationships between maladaptive trait facets and illusion sensitivity scores.**
**Based on prior research (Makowski et al., 2023), we expect to find evidence (BF10 ≥ 3) supporting a relationship between the psychoticism facet of the PID-5 and illusion sensitivity.**
Data analysis will be carried out using R, using *tidyverse* [@tidyverse] and *easystats* [@easystats; @parameters; @correlation; @bayestestR; @datawizard]. 
The analysis script and additional information are available at **https://osf.io/da3u6/?view_only=247d4efa1afe456aa07662732946d4e6** [Note this link will be replaced with the GitHub page of the current project upon completion of the review process to ensure continued anonymisation].

@@

All the study materials, experiment, data, and analysis is available on GitHub. [For the review process the pcs materials, the illusion game, and the analyses scripts can be accessed here: **https://osf.io/da3u6/?view_only=247d4efa1afe456aa07662732946d4e6**. Note this link will be replaced with the GitHub page of the current project upon completion of the review process to ensure continued anonymisation].
